AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-15 Latex/Paper/main.tex
Rework introduction

For this research paper we looked into the topic of generating a drum transcription from a piece of music containing a recording of a drum kit.
Drum transcription is considered a classical music information retrieval (MIR) problem, where you want to extract information from a mixed piece of music.
In order to achieve this an algorithm is applied to the raw sound data to find the time points where a drum event happens in the song.
This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
While in theory this can be used to find any kind of percussive event within a musical piece, we focused mainly on base drum hits in our research.

The transcription of the drum track of a song can be useful in many cases.
The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also a integral part.
Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm. [QUELLE]
Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.

On first sight extracting the time point of a drum hit for a polyphonic, mixed piece of music sounds like a difficult task.
In fact though there are multiple mathematically simple algorithm to achieve that.
For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).
NMF is in its essence a pattern matching algorithm.
It decomposes the magnitude spectrum of a song into two matrices.
The first one contains the magnitude spectra of the individual components and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}

@@

>>>>

For this research paper we looked into the topic of generating a drum transcription from a piece of music containing a recording of a drum kit.
Drum transcription is considered a classical music information retrieval (MIR) problem, where you want to extract information from a mixed piece of music.
In order to achieve this an algorithm is applied to the raw sound data to find the time points where a drum event happens in the song.
This list of time points and a corresponding flag with the kind of the drum event is called the drum transcription. 
While in theory this can be used to find any kind of event within a musical piece, we focused mainly on basic drum sounds in our research.

The transcription of the drum track of a song can be useful in many cases.
The simplest would be to generate the sheet music for a song where the original has been lost or is not available.
It can also be used for more sophisticated use cases like a conversion of a audio file to a MIDI sequence (known as Audio-to-MIDI).
For syncing visuals to music in VJing or light show applications (Sound-to-Light) a drum transcription is also an integral part.
Furthermore the drum transcription of a song can be used as a basis for more complicated MIR analysis.
For example using the results of the drum transcription a Beats per Minute (BPM) detection can be build, which in turn can then be the basis of a tempo detection algorithm [QUELLE].
Overall the drum transcription of a song is a basic but versatile information, that can be used in many different applications.

On first sight extracting the time point of a drum hit for a polyphonic, mixed piece of music sounds like a difficult task.
In fact though there are multiple mathematically simple algorithm to achieve that.
For this research we took an algorithm commonly used for these kind of problems: the non-negative matrix factorization (NMF).

In section \ref{sec:algo} there will be a detailed explanation of how NMF works.

@@

NMF is in its essence a pattern matching algorithm.
It decomposes the magnitude spectrum of a song into two matrices.
The first one contains the magnitude spectra of the individual components we are interested in and the second one contains the time-varying gain of these components, which tells us when each of the components for the first matrix is active.
The sum of both matrices makes up an approximation of the original spectrum. \cite{virtanen2007}
